Puyuma: Linux-based RTOS experimental platform for constructing self-driving miniature vehicles

### 2017-04-20 cthpc-2017/puyuma.tex
add abstract

\title{Title}

@@

\begin{abstract}
\end{abstract}

>>>>

\title{Puyuma: Linux-based RTOS experimental platform for constructing self-driving miniature vehicles}

@@

\begin{abstract}
A holistic design and cost-efficient platform to construct self-driving systems is presented, with an emphasis on Linux-based software architectures for computer vision, control system, and inter-vehicle communication. Starting with an executable specification of autonomous car application, subsequent transformations are performed across different levels of abstraction until the final implementation is achieved. The software partitioning is facilitated through the integration of ROS and OpenCV in the same design environment, as well as closed-loop control algorithms and Linux in the run-time system. We built a rapid prototyping based on fundamentally open source technologies, bill of material (BOM) under 100 dollars USD, which allows developers to be explored and evaluated in realistic conditions efficiently. Using lane departure and the corresponding performance speedup, we show that our platform reduces the design time, while improving the verification efforts, with the aid of tweaked real-time executives.
\end{abstract}
